The Ultraviolet Radiation Environment of a Tropical Megacity in Transition: Mexico City 2000-2019

### 2021-07-13 Paper_third_version/Article_UV_Mexico.tex
Merge

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The document title should be given as usual. Some journals require
%% a running title from the author: this should be supplied as an
%% optional argument to \title.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title[The UV radiation in Mexico City]
  {The Ultraviolet Radiation Environment of a Tropical Megacity in Transition: Mexico
  City 2000-2019}

@@

The UV Index data derived from satellite-based measurements
were used for comparison with the ground-based measurements.
These data were provided by the Ozone Monitoring
Instrument (OMI)~on board of AURA-NASA satellite.\citep{dcio} OMI
is operated collaboratively by the Netherlands Agency for Aerospace
Programmes (NIVR), the Finnish Meteorological Institute (FMI) and NASA.
OMI performs observations over a geographical area of 13$\times$24km\textsuperscript{2} at nadir. For
the coordinates (19.33°N, 99.18°W) and elevation (2268 m asl) of Mexico City,
the satellite overpass time is between 19:00h - 21:00h UTC (20:00h - 22:00h CET).
The OMI instrument measures reflected and backscattered radiances of the atmosphere-surface system at several UV wavelengths. The ozone column is estimated by differential absorption of several adjacent
wavelengths in the O\textsubscript{3} Huggins band\citep{Veefkind_2006}, and is used in a radiative transfer model to estimate clear-sky UVI at the surface. Clouds are estimated from the observed reflectivity at a wavelength not affected by O\textsubscript{3} absorption (360 nm) and the clear-sky UVI is adjusted for their presence. A correction for absorbing aerosols is made using a global aerosol climatology.\citep{Arola_2009}
The UV Index used for Mexico City corresponds to values at local noon time and clear sky
from OMUVB Level 2 OVP data product, version 1.3 and collection 3.

@@

\begin{figure}[H]
  \centering
  \includegraphics[scale=0.5]{figures/Monthly_mean_RD.png}
  \caption{Deviation (\%) of satellite-derived UVI from the ground-based monthly means UVI for the period 2005-2019.}
  \label{fig:percentage_relative_difference}
\end{figure}

Figure \ref{fig:percentage_relative_difference} deviation of the OMI-derived UVI from the ground-based monthly averages. The mean percentage relative difference
was 35\% in the period 2005-2019. Comparable UV reductions, of 30-40\% due to aerosols, were reported by
\citet{Panicker_2009} over Pune, India from April 2004 to
March 2005, with sensitivity coefficients (i.e. change in UVI per unit
change in AOD) similar to those found here in Table~\ref{table:TUVmodel}.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The document title should be given as usual. Some journals require
%% a running title from the author: this should be supplied as an
%% optional argument to \title.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title[The UV Radiation in Mexico City]
  {The Ultraviolet Radiation Environment of a Tropical Megacity in Transition: Mexico
  City 2000-2019}

@@

The UV Index data derived from satellite-based measurements
were used for comparison with the ground-based measurements.
These data were provided by the Ozone Monitoring
Instrument (OMI)~on board of AURA-NASA satellite.\citep{dcio} OMI
is operated collaboratively by the Netherlands Agency for Aerospace
Programmes (NIVR), the Finnish Meteorological Institute (FMI) and NASA.
OMI performs observations over a geographical area of 13$\times$24km\textsuperscript{2} at nadir. For
the coordinates (19.33°N, 99.18°W) and elevation (2268 m asl) of Mexico City,
the satellite overpass time is between 19:00h - 21:00h UTC (20:00h - 22:00h CET).
The OMI instrument measures reflected and backscattered radiances of the atmosphere-surface system at several UV wavelengths.\cite{Tanskanen_2006} The ozone column is estimated by differential absorption of several adjacent
wavelengths in the O\textsubscript{3} Huggins band\citep{Veefkind_2006}, and is used in a radiative transfer model to estimate clear-sky UVI at the surface. Clouds are estimated from the observed reflectivity at a wavelength not affected by O\textsubscript{3} absorption (360 nm) and the clear-sky UVI is adjusted for their presence.\cite{Tanskanen_2007} A correction for absorbing aerosols is made using a global aerosol climatology.\citep{Arola_2009}
The UV Index used for Mexico City corresponds to values at local noon time and clear sky
from OMUVB Level 2 OVP data product, version 1.3 and collection 3.

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=0.71\columnwidth]{figures/Monthly_mean_RD.png}
  \caption{Deviation (\%) of satellite-derived UVI from the ground-based monthly means UVI for the period 2005-2019.}
  \label{fig:percentage_relative_difference}
\end{figure}

Figure \ref{fig:percentage_relative_difference} shows the deviation of the OMI-derived UVI from the ground-based monthly averages. The mean deviation
was 35\% in the period 2005-2019. Comparable UV reductions, of 30-40\% due to aerosols, were reported by
\citet{Panicker_2009} over Pune, India from April 2004 to
March 2005, with sensitivity coefficients (i.e. change in UVI per unit
change in AOD) similar to those found here in Table~\ref{table:TUVmodel}.
